---
title: "Control Flows"
format: html
editor: visual
---

## Loading Files

```{r}
load("files/hw2_list.rda")
```

## Task 1: Control Flow Practice

We are creating a status column in the data frames within the list

```{r}
bp_list$treatment$status <- character(20)
bp_list$placebo$status <- character(10)
```

For the our dataframes (within the list), we are creating a for loop that follows the sequential logic of optimal (≤ 120), borderline (120 < bp ≤ 130), and high (> 130) to assign to the "status" column based on "post_bp"

We can accomplish this by fetching the post_bp value for that record and updating the status value using a nested if/else statement.

```{r}
for (i in 1:nrow(bp_list$placebo)){
  record_post_bp <- bp_list$placebo$post_bp[i]
  if (record_post_bp <= 130){
    if (record_post_bp <= 120) {
      record_status <- "optimal"
    } else {
      record_status <- "borderline"
    }
  } else {
    record_status <- "high"
  } 
  bp_list$placebo$status[i] <- record_status
}

for (i in 1:nrow(bp_list$treatment)){
  record_post_bp <- bp_list$treatment$post_bp[i]
  if (record_post_bp <= 130){
    if (record_post_bp <= 120) {
      record_status <- "optimal"
    } else {
      record_status <- "borderline"
    }
  } else {
    record_status <- "high"
  } 
  bp_list$treatment$status[i] <- record_status
}
```

## Task 2: Function Writing